Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-23 ATVA 2025/formula.tex
update

Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
%(this can be obtained very efficiently by {\em one} call to an LP solver).
Function
$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
%Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
%$\Improve\_\min^z(n)$. 
Computing exactly $\Improve\_\max^z(n)$ would need a MILP call on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$, which would be very time consuming. Instead, the SAS function uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ 
(Fig. \ref{fig_table3}).

>>>>

Consider $(\sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
%(this can be obtained very efficiently by {\em one} call to an LP solver).
Function
$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
%Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
%$\Improve\_\min^z(n)$. 
Computing exactly $\Improve\_\max^z(n)$ would need a MILP call on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$, which would be very time consuming. Instead, the SAS function uses a (single) LP call to compute $(\sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ 
(Fig. \ref{fig_table3}).
